---
title: "Titanic App Introduction"
author: "yi zheng"
date: "July 31, 2017"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
source('EDA.R')
```

## Agenda

- Background
- Titanic Dataset
- Read Me
- App link

## Background

This shiny app is build on titanic dataset, an introduction dataset used mostly for machine learning introduction.  
It contains the data for all the passanger of the titanic 891 with 8 variable.  
The application is also a dashboard to show the explortary analysis as well as the result of three popular machine learning algorithm prediction

## Data

```{r,echo=FALSE}
summary(traindf1)
```

## Dashboard Readme

- In the first tab, you could see the whole dataset
- In the second tab, you could view the numeric distribution of the dataset
- In the third tab, there is selection to see the machine learning prediction of the dataset

## Application Link
This is the link to the application
[Here](https://hehe233.shinyapps.io/TitanicPrediction/)
